Comparing MTurk and the US Population's Occupational Diversity

### 2018-09-21 Manuscript.Rmd
Updated code to work with my computer. I also included directions / requests for effect size indicators.

##Replication Demographic Analaysis
##Age Analysis
```{r}
#Age Analysis T- Test
#Load Dataset
require(dplyr)
require(readxl)
BLS_age <- read_excel("age_demo.xlsx")

@@

#Define sample mean
MTurk17 <- read_excel("~/MTurk Diversity 2017 Data/2017 Data.xls")
samp_mean <- as.numeric(MTurk17 %>%
  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))

@@

#Run t test.
t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
View(t_value)
```

@@

#Sum chi-square values.
sum(gender_ch2$chi2, na.rm=TRUE)
```

>>>>

##Replication Demographic Analaysis
##Age Analysis
```{r}
#Age Analysis T- Test
#Load Dataset
require(dplyr)
require(readxl)
age_demo <- read_excel("age_demo.xlsx")

@@

#Define sample mean
MTurk17 <- read_excel("2017 Data.xls")
samp_mean <- as.numeric(MTurk17 %>%
  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))

@@

#Run t test.
t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
t_value

#So MTurk is much younger than the population on average. We need to convert this to an effect size (Cohen's D). 
```

@@

#Sum chi-square values.
sum(gender_ch2$chi2, na.rm=TRUE)

#So it appears that MTurk is largely dominated by females. We need to have an effect size describing this phenomena (e.g., a likelihood ratio).
```
